---
output: rmarkdown::github_document
---

# crumpets

Tools to Work with and Manage 'gitea'

## Description

The 'gitea' project is a 'GitHub'-/'GitLab'-like web user interface
to 'git' repositories. Methods are provided to access and administer 'gitea'
programmatically.

## NOTE

The function skeletons were generated from the Swagger definition file for Gitea.
These will be incrementally fully formed and the ones that are still a WIP will
hard error with a `stop()` message. Function titles prefied with `WIP` are WIP and 
you're welcome to join in the fun of building out 146 `httr` functions O_o.

## What's Inside The Tin

_There are at least 140 functions in this package so please see the manual pages in the online R help system._

The following functions are implemented (i.e. are not in a WIP status):

- `get_version`:  Returns the version of the Gitea application
- `repo_migrate`:  Migrate a remote git repository
- `repo_mirror_sync`: Sync a mirrored repository
- `user_current_list_repos`:  List the repos that the authenticated user owns or has access to
- `user_get`:  Get a user
- `user_get_current`:  Get the authenticated user
- `user_list_repos`:  List the repos owned by the given user

## Installation

```{r eval=FALSE}
devtools::install_git("git://gitlab.com/hrbrmstr/crumpets")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(crumpets)

# current verison
packageVersion("crumpets")

```

```{r}
get_version()
```